CS6110: Software Verification Final Project: Formal Verification of Rust Programs with Creusot

### 2023-05-05 paper.tex
Fix URLs

Why3 describes itself as ``a platform for deductive program verification''\footnote{https://why3.lri.fr/}---instead of an interactive theorem prover like Coq or the like, Why3 is a layer above and focuses on automating the use of such provers.\cite{bobotWhy3ShepherdYour}
Why3 provides a language---called WhyML---that can be translated into languages a multitude of theorem provers can understand.
This is neat because we every prover has its strengths---Coq will be a better fit for certain proofs than fully-automated provers, whereas some provers will work without the laborious intervention that Coq requires.
Why3 allows us to have it all.

@@

This is an incredibly simple example; we will leave a full description of what the language can do to the specification\footnote{https://why3.lri.fr/doc/syntaxref.html}, but suffice it to say that WhyML has all of the language constructs that you would expect from a formal logic system.

@@

We have to use the ZArith module from the Coq standard library\footnote{} because Why3 works with integers, not naturals.
We can add this line after the \texttt{intros x.} to get Coq to accept the proof:

@@

To be fair, the authors of Creusot \emph{do} point out that this is unstable research software.\footnote{https://github.com/xldenis/creusot#about}
If your work can tolerate frequent breakage, this might be a good option for you right now.
Neither of us would use this in its current form though---once things stabilize, however, Creusot will be a formidable addition to Rust's already substantial clout in the reliable software space.

>>>>

Why3 describes itself as ``a platform for deductive program verification''\footnote{\url{https://why3.lri.fr/}}---instead of an interactive theorem prover like Coq or the like, Why3 is a layer above and focuses on automating the use of such provers.\cite{bobotWhy3ShepherdYour}
Why3 provides a language---called WhyML---that can be translated into languages a multitude of theorem provers can understand.
This is neat because we every prover has its strengths---Coq will be a better fit for certain proofs than fully-automated provers, whereas some provers will work without the laborious intervention that Coq requires.
Why3 allows us to have it all.

@@

This is an incredibly simple example; we will leave a full description of what the language can do to the specification\footnote{\url{https://why3.lri.fr/doc/syntaxref.html}}, but suffice it to say that WhyML has all of the language constructs that you would expect from a formal logic system.

@@

We have to use the ZArith module from the Coq standard library\footnote{\url{https://coq.inria.fr/library/Coq.ZArith.BinInt.html}} because Why3 works with integers, not naturals.
We can add this line after the \texttt{intros x.} to get Coq to accept the proof:

@@

To be fair, the authors of Creusot \emph{do} point out that this is unstable research software.\footnote{See the README of the Creusot\cite{denisCreusot2023} repository for this warning.}
If your work can tolerate frequent breakage, this might be a good option for you right now.
Neither of us would use this in its current form though---once things stabilize, however, Creusot will be a formidable addition to Rust's already substantial clout in the reliable software space.
